### 2009-12-14 docs/marcello-dissertation/thesis/chapter9-conclusions-and-future-works.tex
Reviews of misspelling and references to pages, Section, etc.
- Chapter 7: Fixes on "Chapter" to chapter
- Chapter 8: Subversion Conflict line removal, and other fixes
- Appendix: Removing "on page x" for the image on the same page.

git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@706 559edde2-a4d4-44e0-96fc-4035e40d7396

There were significant trends covered in this work, including the importance
that sensor networks are becoming ubiquitous, having their produced data
available online and other types of media. In the scope of Environmental Sensor
Networks, the collected data is the most important parameter to real-world
applications based on sensor networks. For example, the data collected in the
water may determine if a river is polluted, while the data collected during a
heavy snowfall can indicate hazard alerts the population. However, in order to
provide access to the collected data, one must first assess the different types of
infrastructural characteristics of the studied sensor networks. The selection
of a technology that provides such a persistence solution capabilities can be
part of a process of analysis of taxonomies proposed by this work,
characterized as the first contribution of this report.

@@

As far as future works, there are many different directions for exploration.
The first major release of mongoDB with complete support to shards is
scheduled for 2010. An important mechanism of mongoDB is that it can
manage different mongoDB servers spread out in a cluster. This feature will give
better support to the Data-Centric Storage approach. This approach can reduce
the retrieval time by focusing on centralized selection of data over a given
database shard. Moreover, the overall search through the collected data
attributes can be drastically decreased by a parallel search over the database
shards using the MapReduce \cite{map-reduce} tools. At the time of development
of the experiments, the MapReduce API from mongoDB was also in the alpha
version, and therefore, presented many bugs. One suggestion for the
implementation of such functionality is based in Figure
\ref{fig:future-works-data-centric-map-reduce} (\cite{map-reduce-notes}), which
shows an architectural idea of the deployment of a Data-Centric storage approach. One scenario of
data retrieval is when a given processing in the search results are
required to be executed in parallel. The task of querying broken down into
two phases: the definition of the reduced problem as the parts, and the
mapping of the final result calculated with the response from each part. If
``Task" is considered to be a query (arrow 1) tor the server, then the
execution of the same query occurs in all different partitions (arrow 2), or
mongoDB shards. After processing the request, each node returns the result of
the query to the server (arrow 3), whose responsibility is to process each
individual result and return the final Result to the client application (arrow
4).

>>>>

There were significant trends covered in this work, including the importance
that sensor networks are becoming ubiquitous, having their produced data
available online and other types of media. In the scope of Environmental Sensor
Networks, the collected data is the most important parameter to real-world
applications based on sensor networks. For example, the data collected in the
water may determine if a river is polluted, while the data collected during a
heavy snowfall can indicate hazard alerts to the population. However, in order
to provide access to the collected data, one must first assess the different types of
infrastructural characteristics of the studied sensor networks. The selection
of a technology that provides such a persistence solution capabilities can be
part of a process of analysis of taxonomies proposed by this work,
characterized as the first contribution of this report.

@@

As far as future works, there are many different directions for exploration.
The first major release of mongoDB with complete support to shards is
scheduled for 2010. An important mechanism of mongoDB is that it can
manage different mongoDB servers spread out in a cluster. This feature will give
better support to the Data-Centric Storage approach. This approach can reduce
the retrieval time by focusing on centralized selection of data over a given
database shard. Moreover, the overall search through the collected data
attributes can be drastically decreased by a parallel search over the database
shards using the MapReduce \cite{map-reduce} tools. At the time of development
of the experiments, the MapReduce API from mongoDB was also in the alpha
version, and therefore, presented many bugs. One suggestion for the
implementation of such functionality is based in Figure
\ref{fig:future-works-data-centric-map-reduce} (\cite{map-reduce-notes}), which
shows an architectural idea of the deployment of a Data-Centric storage
approach. One scenario of data retrieval is to process search results
required to be executed in parallel. The task of querying broken down into
two phases: the definition of the reduced problem as the parts, and the
map of the final result calculated with the response from each part. If
``Task" is considered to be a query (arrow 1) to the server, then the
execution of the same query occurs in all different partitions (arrow 2), or
mongoDB shards. After processing the request, each node returns the result of
the query to the server (arrow 3), whose responsibility is to process each
individual result and return the final one to the client application (arrow
4).
